### 2015-02-05 paper/main.tex
updated dsc to new format

Here we consider one setting in which FDR-based methods are widely used:
an experimenter has measured a large numbers of ``effects", each with an associated
measurement precision (standard error), 
and the goal is to identify which of the effects we can declare to be non-zero (with some prescribed level of confidence), and also
to provide estimates -- both point estimates and interval estimates -- for these effects.
This setting arises commonly in many areas of statistics, and particularly in genomics applications.
For example, in genomics
a common goal is to identify ``differentially-expressed genes" -- that is, genes
whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
expression level between the two conditions, often referred to as the ``log-fold change". 
%Measurement precision will often vary among genes --  for example, log-fold change estimate for highly expressed genes may have greater precision than those for lower-expressed genes -- and one goal  of our methods is to allow for thiis variation.

@@

Many tools have been developed for estimating or controlling the FDR and related quantities \cite{}, and several are widely used.
Here we present new tools that bring two important new ideas to bear on the problem.
First, these tools are designed to take account of variations in the {\it measurement precision} of different effects, reducing the influence of low-precision measurements.
For example, in the example of detecting differentially expressed genes, measurements of log fold change for high-expressed genes 
may have better precision than those for low-expressed genes; by incorporating this information our methods can avoid the tendancy for 
imprecise measurements at low-expressed genes to dilute the signal at higher-expressed genes.
Second, our tools explicitly assume that the non-zero effects have a unimodal distribution centered at zero. This assumption 
is, we argue, often realistic, and comes with considerable benefits, both statistical and computational. 
Our tools are implemented in an R package \ashr (short for ``Adaptive Shrinkage") and we 
demonstrate how the incorporation of these two ideas can lead to a substantial reduction in estimated FDRs (or, equivalently,
a substantial increase in the number of discoveries at a given FDR).

Although we motivate our tools by the need to address the FDR problem, our \ashr package, as its name suggests, 
provides a general tool for shrinkage estimation. Shrinkage estimation is a powerful tool, with many potential applications, including for example wavelet denoising, 
where shrinkage of wavelet coefficients is used to smooth signals. 
However, in contrast to FDR methods, shrinkage methods are not so widely used in practice, at least in the kinds
of genomics settings I am familiar with. One possible reason for this is that most work on shrinkage-based estimation has focussed
on point estimates, rather than on interval estimates which are often of more direct practical relevance. Another contributing
factor may be the paucity of general-purpose software packages for this kind of shrinkage estimation.
 (There are, perhaps, more packages for shrinkage esitmation in the more complex setting of covariance estimation, where shrinkage is perhaps still more important.)
Our work here addresses both these issues, providing a general-purpose software tool that uses shrinkage ideas to improve both
point and interval estimates.

@@

\begin{figure}
\center \includegraphics[height=6in]{Rcode/figures/decomp_ZA.pdf}
\caption{Comparison of the way that different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (light blue). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) assumes that the effect sizes (and thus the $z$ scores) have a unimodal distribution about 0, resulting in a very different decomposition that in this case is much closer to the truth. (These data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything light blue.)} \label{fig:ZA}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[][Histograms of $p$ values for good-precision, poor-precision, and combined observations]{
\includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_hist.pdf} 
    \label{fig:goodpoor-hist}
} \\
\subfloat[][Comparison of results of different methods applied to good-precision observations only ($x$ axis) and combined data ($y$ axis). Each point shows the estimated error rate ($q$ value, lfdr, or lfsr) for a good-precision observation under the two different analyses.]{
\includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_scatter.pdf}
    \label{fig:goodpoor-scatter}
}
\caption{Simulated illustration how poor-precision observations can contaminate signal from good-precision observations. The top panel (a) illustrates that when 
$p$ values from good-precision observations (left) and from poor-precision observations (center) are combined (right), they produce
a distribution of $p$ values with less overall signal - and so, by conventional methods, will give a higher estimated FDR at any given threshold.
The bottom panel (b) illustrates this behaviour directly for the methods \qvalue and \locfdr: the $q$-values from \qvalue and the lfdr estimates from \locfdr are higher when applied to all data than when applied to good-precision observations only. In contrast the methods described here (\ashr) produce effectively the same results (here, the lfsr) in the good-precision and combined data analyses.} \label{fig:goodpoor}
\end{figure}

@@

\begin{figure}[!ht] \label{fig:good_poor_hist}
\begin{center}
\includegraphics[height=3in]{Rcode/figures/good_poor_hist.pdf}
\includegraphics[width=6.5in]{Rcode/figures/good_vs_all.pdf}
\end{center}
\caption{}
\end{figure}

@@

We simulated data under three scenarios for the underlying effect size distribution $g$:
\begin{enumerate}
\item[Scenario A:]
A mixture of zero-centered normals,
\begin{equation}
g(\cdot) =  (2/3) N(\cdot; 0,1) + (1/3) N(\cdot; 0, 2^2)
\end{equation}
\item[Scenario B:]
A symmetric ``flat-topped" distribution, designed to be difficult to capture by a mixture of zero-centered normals 
\begin{equation}
g(\cdot) = (1/7) [N(\cdot; -1.5, 0.5^2) + N(\cdot; -1, 0.5^2) + N(\cdot; 0.5, 0.5^2) + N(\cdot; 0, 0.5^2) + N(\cdot; 0.5, 0.5^2) + N(\cdot; 1, 0.5^2) + N(\cdot; 1.5, 0.5^2)]
\end{equation}
\item[Scenario C:]
An asymmetric distribution, 
\begin{equation}
g(\cdot) = (1/4) N(\cdot; -2 ,2^2) + (1/4) N(\cdot; -1 ,1.5^2) + (1/3) N(\cdot; 0 ,1) + (1/6) N(\cdot; 1,1) 
\end{equation}
\end{enumerate}
In each case we simulated $\bhat_j  = \beta_j + N(0,s^2_j=1)$.

@@

This work was supported by NIH grant .

>>>>

Here we consider one setting in which FDR-based methods are widely used:
an experimenter has measured a large numbers of ``effects", each with an associated
measurement precision (standard error), 
and the goal is to identify which of the effects we can declare to be non-zero, with some prescribed level of confidence.
Although the usual focus of FDR-based methods is on distinguishing zero and non-zero effects,
here we also focus on providing estimates -- both point estimates and interval estimates -- for these effects.
This setting arises commonly in many areas of statistics, and particularly in genomics applications.
For example, in genomics
a common goal is to identify ``differentially-expressed genes" -- that is, genes
whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
mean expression level between the two conditions, often referred to as the ``log-fold change". 
%Measurement precision will often vary among genes --  for example, log-fold change estimate for highly expressed genes may have greater precision than those for lower-expressed genes -- and one goal  of our methods is to allow for thiis variation.

@@

Many tools have been developed for estimating or controlling the FDR and related quantities \cite{}, and some are widely used.
Here we present new tools that bring two important ideas to bear on the problem.
First, these tools are designed to take account of variations in the {\it measurement precision} of different effects, reducing the influence of low-precision measurements.
For example, in the example of detecting differentially expressed genes, measurements of log fold change for high-expressed genes 
may have better precision than those for low-expressed genes; by incorporating this information our methods can avoid the tendancy for 
imprecise measurements at low-expressed genes to dilute the signal at higher-expressed genes.
Second, our tools explicitly assume that the non-zero effects have a unimodal distribution centered at zero. This assumption 
is, we argue, often realistic, and comes with considerable benefits, both statistical and computational. 
Our tools are implemented in an R package \ashr (short for ``Adaptive Shrinkage") and we 
demonstrate how the incorporation of these two ideas can lead to a substantial reduction in estimated FDRs (or, equivalently,
a substantial increase in the number of discoveries at a given FDR).

Although we motivate our tools by the need to address the FDR problem, our \ashr package, as its name suggests, 
provides a general tool for shrinkage estimation. Shrinkage estimation is a powerful tool, with many potential applications, including for example wavelet denoising, 
where shrinkage of wavelet coefficients is used to smooth signals. 
However, in contrast to FDR methods, shrinkage methods are not so widely used in practice, at least in the kinds
of genomics settings I am familiar with. One possible reason for this is that most work on shrinkage-based estimation has focussed
on point estimates, rather than on interval estimates which are often of more direct practical relevance. Another contributing
factor may be the paucity of general-purpose software packages for this kind of shrinkage estimation.
% (There are, perhaps, more packages for shrinkage estimation in the more complex setting of covariance estimation, where shrinkage is perhaps still more important.)
Our work here addresses both these issues, providing a general-purpose software tool that uses shrinkage ideas to improve both
point and interval estimates.

@@

\begin{figure}
\center \includegraphics[height=6in]{Rcode/figures/decomp_ZA.pdf}
\caption{Comparison of the way that different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (light blue). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) assumes that the effect sizes (and thus the $z$ scores) have a unimodal distribution about 0, resulting in a very different decomposition that in this case is much closer to the truth. (These data were simulated under a model where all of the effects are non-zero -- specifically, $\beta_j \sim N(0,1)$, $s_j=1$, resulting in $z_j \sim N(0,2)$ -- so the ``true" decomposition would make everything light blue.)} \label{fig:ZA}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[][Density histograms of $p$ values for good-precision, poor-precision, and combined observations]{
\includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_hist.pdf} 
    \label{fig:goodpoor-hist}
} \\
\subfloat[][Comparison of results of different methods applied to good-precision observations only ($x$ axis) and combined data ($y$ axis). Each point shows the estimated error rate ($q$ value, lfdr, or lfsr) for a good-precision observation under the two different analyses.]{
\includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_scatter.pdf}
    \label{fig:goodpoor-scatter}
}
\caption{Simulation illustrating how poor-precision observations can contaminate signal from good-precision observations. The top panel (a) illustrates that when 
$p$ values from good-precision observations (left) and from poor-precision observations (center) are combined (right), they produce
a distribution of $p$ values with less overall signal - and so, by conventional methods, will give a higher estimated FDR at any given threshold.
The bottom panel (b) illustrates this behaviour directly for the methods \qvalue and \locfdr: the $q$-values from \qvalue and the lfdr estimates from \locfdr are higher when applied to all data than when applied to good-precision observations only. In contrast the methods described here (\ashr) produce effectively the same results (here, the lfsr) in the good-precision and combined data analyses.} \label{fig:goodpoor}
\end{figure}

@@

PENN Note: need to fix bug in dscr where when an element of result is null, the data.frame command doesn't work.
Want to convert it to missing - maybe in the scoring function.

@@

We simulated data under three scenarios for the underlying effect size distribution $g$:
\begin{enumerate}
\item[Scenario A:]
A mixture of zero-centered normals,
\begin{equation}
g(\cdot) =  (2/3) N(\cdot; 0,1) + (1/3) N(\cdot; 0, 2^2)
\end{equation}
\item[Scenario B:]
A symmetric ``flat-topped" distribution, designed to be difficult to capture by a mixture of zero-centered normals 
\begin{equation}
g(\cdot) = (1/7) [N(\cdot; -1.5, 0.5^2) + N(\cdot; -1, 0.5^2) + N(\cdot; -0.5, 0.5^2) + N(\cdot; 0, 0.5^2) + N(\cdot; 0.5, 0.5^2) + N(\cdot; 1, 0.5^2) + N(\cdot; 1.5, 0.5^2)]
\end{equation}
\item[Scenario C:]
An asymmetric distribution, 
\begin{equation}
g(\cdot) = (1/4) N(\cdot; -2 ,2^2) + (1/4) N(\cdot; -1 ,1.5^2) + (1/3) N(\cdot; 0 ,1) + (1/6) N(\cdot; 1,1) 
\end{equation}
\end{enumerate}
In each case we simulated $\bhat_j  = \beta_j + N(0,s^2_j=1)$.

@@

This work was supported by NIH grant xxx and a grant from the Gordon and Betty Moore Foundation.
